---
title: "Simulation Exercise Instructions"
author: "HPSUN"
date: "2017-12-3"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Overview
This project is about to test Central Limit Theorem with  exponential distribution using R simulation.  
I will set like a thousand simulations and compare the mean and variance from sample to the theoretical mean and variance.
## Simulations
In the simulation, n is set to 40, lambda set to 0.2.
```{r}
n <- 40
lambda <- 0.2
```
let's run 10000 simulations and store the means and variances of samples.
```{r}
sample_mean <- NULL
for (i in 1:10000){
    sample_mean <- c(sample_mean, mean(rexp(n,lambda)))
}
```
##Sample Mean versus Theoretical Mean
```{r}
hist(sample_mean,main="Histogram of Sample Mean",xlab="")
abline(v=(lambda^-1),col="red",lwd=3)
```

The means of sample are showed as a histograph, the red line indicates the the theoretical mean. And the means of sample mean is very close to the theoretical mean, see below.
```{r}
#theoretical mean
lambda^-1
#mean of means
mean(sample_mean)
#difference
diff(c(lambda^-1,mean(sample_mean)))
```
## Sample Variance versus Theoretical Variance
```{r}
#variance of sample mean
var(sample_mean)
#theoretical variance
lambda^-2/n 
#difference
diff(c(var(sample_mean),lambda^-2/n))
```
The variace of sample mean is very close to the theoretical variance too.
## Distribution
Let's compare the distribution of sample means and a normal distribution of sample mean and sample sd.  
```{r}
hist(sample_mean, prob=TRUE, main="mean distribution for rexp()", breaks=20)
lines(density(sample_mean), lwd=3, col="blue")
curve(dnorm(x,mean=mean(sample_mean), sd=sd(sample_mean)),add = T,col="red", lwd=3, lty = "dotted", yaxt="n")
```
 
From the graph, we found the distribution of sample means is very similar to a normal distribution.That is what Central Limit Theorem told us: The averages are approximately normal, with distributions centered at the population mean and standard deviation equal to the standard error of the mean.So the 95% confidence interval of sampel means can be calcualate as follow:
```{r}
mean(sample_mean) + c(-1,1)*qnorm(.975)*sqrt(var(sample_mean)/n)
```

